---
title: "Conflict Dashboard"
output: 
  flexdashboard::flex_dashboard:
    orientation: columns
    vertical_layout: fill
runtime: shiny
---

```{r setup, include=FALSE}
library(flexdashboard)
library(shiny)
library(rmarkdown)
library(knitr)
library(Hmisc)
library(ggplot2)
library(dplyr)
library(data.table)
library(scales)
library(rgdal)
library(lubridate)

assignInNamespace(x = "cedta.override", value = c(data.table:::cedta.override,"rmarkdown"), ns = "data.table")

opts_chunk$set(echo = FALSE, comment="", warning = FALSE, message = FALSE, tidy.opts=list(width.cutoff=55), tidy = TRUE)

data = fread("D:/Columbia/Spring 2019/Data Science and Public Policy/Final Project/aa_final_full.csv")

price_data = fread("D:/Columbia/Spring 2019/Data Science and Public Policy/Final Project/clean_wfp_food_prices_senegal.csv")

myshp <- "D:\\Columbia\\Spring 2019\\Data Science and Public Policy\\Final Project\\SEN_adm_2\\SEN_adm2.shp"
myfile <- readOGR(myshp)
mydf <- fortify(myfile)

theme_bare <- theme(
  axis.line = element_blank(), 
  axis.text.x = element_blank(), 
  axis.text.y = element_blank(),
  axis.ticks = element_blank(), 
  axis.title.x = element_blank(), 
  axis.title.y = element_blank(),
  legend.text=element_text(size=10),
  legend.title=element_text(size=12),
  panel.background = element_blank(),
  panel.border = element_rect(colour = "gray", fill=NA, size=0.5)
)

theme_common <- theme(
  axis.ticks.y = element_blank(),
  axis.ticks.x = element_blank(),
  axis.text=element_text(size=14),
axis.title=element_text(size=14)
) 

```
Introduction
==================================================

This is the Conflict Dashboard which provides analysis of Conflict incidents in Senegal

This analysis had data for `r sum(data[ACTION_ANY >= 1][,ACTION_ANY])` conflicts that happenend between the years 
`r min(data[,YEAR])` and `r max(data[,YEAR])`


Area - Distrubution
==================================================

Row {data-heights = 400}
-----------------------------------------------------------------------

```{r}
areas <- c("Region","Department")

inputPanel(
  selectInput(inputId = "check_area", label = "Select Area:", choices = areas, selected = areas[1]),
  sliderInput(inputId = "area_date", label = "Year Range", min = min(data[,YEAR]), max = max(data[,YEAR]), value = c(min(data[,YEAR]),max(data[,YEAR])), step = 1)
  
)

renderPlot({

  
  
  if(input$check_area == "Region"){
  state_data <- data[ACTION_ANY >= 1 & YEAR >= input$area_date[1]  & YEAR <= input$area_date[2]] %>%
    group_by(NAME_1) %>%
    summarise(count = sum(ACTION_ANY))%>% 
    arrange( desc(count),NAME_1)

  ggplot(state_data, aes(x =  reorder(NAME_1,desc(count)), y = count, fill= NAME_1)) +
    geom_bar(position = "dodge", stat = "identity", show.legend = FALSE) +
    theme_common +
    labs(x = "Region", y = "Number of incidents")
    
  }
  else if(input$check_area == "Department"){
    
  district_data <- data[ACTION_ANY >= 1 & YEAR >= input$area_date[1]  & YEAR <= input$area_date[2]] %>%
    group_by(NAME_2) %>%
    summarise(count = sum(ACTION_ANY))%>% 
    arrange( desc(count),NAME_2)

  ggplot(district_data, aes(x =  reorder(NAME_2,desc(count)), y = count, fill= NAME_2)) +
    geom_bar(position = "dodge", stat = "identity", show.legend = FALSE) +
    theme_common +
    labs(x = "Department", y = "Number of incidents")  
    
  }
}
) 

```

Region - Time
==================================================

Row {data-heights = 400}
-----------------------------------------------------------------------


```{r}

state_data <- data[ACTION_ANY >= 1] %>%
    group_by(NAME_1) %>%
    summarise(count = sum(ACTION_ANY))%>% 
    arrange( desc(count),NAME_1)


inputPanel(
  selectInput(inputId = "check_region", label = "Select Region:", choices =state_data$NAME_1, selected = state_data$NAME_1[1]),
  sliderInput(inputId = "region_date", label = "Year Range", min = min(data[,YEAR]), max = max(data[,YEAR]), value = c(min(data[,YEAR]),max(data[,YEAR])), step = 1)
)


renderPlot({
  
year_reg <- data[ACTION_ANY >= 1 & NAME_1 == input$check_region & YEAR >= input$region_date[1]  & YEAR <= input$region_date[2]] %>%
  group_by(YEAR) %>%
  summarise(count = sum(ACTION_ANY))%>% 
  arrange(YEAR)
min_y = max(input$region_date[1], 1990)
max_y = min(input$region_date[2], 2015)
ggplot(year_reg, aes(x =  YEAR, y = count)) +
  geom_count(show.legend = FALSE) +
  theme_common +
  labs(x = "Years", y = "Number of incidents") + 
  scale_y_continuous(breaks= pretty_breaks())+ 
  scale_x_continuous(limits=c(min_y, max_y),breaks= pretty_breaks())
}
) 



```


Department - Time
==================================================

Row {data-heights = 400}
-----------------------------------------------------------------------


```{r}

district_data <- data[ACTION_ANY >= 1] %>%
    group_by(NAME_2) %>%
    summarise(count = sum(ACTION_ANY))%>% 
    arrange( desc(count),NAME_2)


inputPanel(
  selectInput(inputId = "check_dist", label = "Select Region:", choices =district_data$NAME_2, selected = district_data$NAME_2[1]),
  sliderInput(inputId = "dist_date", label = "Year Range", min = min(data[,YEAR]), max = max(data[,YEAR]), value = c(min(data[,YEAR]),max(data[,YEAR])), step = 1)
)


renderPlot({
  
year_dist <- data[ACTION_ANY >= 1 & NAME_2 == input$check_dist & YEAR >= input$dist_date[1]  & YEAR <= input$dist_date[2]] %>%
  group_by(YEAR) %>%
  summarise(count = sum(ACTION_ANY))%>% 
  arrange(YEAR)

min_y = max(input$dist_date[1], 1990)
max_y = min(input$dist_date[2], 2015) 
ggplot(year_dist, aes(x =  YEAR, y = count)) +
  geom_count(show.legend = FALSE) +
  theme_common +
  labs(x = "Years", y = "Number of incidents") + 
  scale_y_continuous(breaks= pretty_breaks())+ 
  scale_x_continuous(limits=c(min_y, max_y),breaks= pretty_breaks())
}
) 



```


<!-- Factors -->
<!-- ================================================== -->

<!-- Row {data-heights = 500} -->
<!-- -------------------------------------------------- -->



<!-- ```{r} -->

<!-- natural_var <-  c("TEMP", "RAIN", "Maize", "Millet", "Rice", "Sorghum", "biomass") -->

<!-- choice <- c("Total", "Average") -->
<!-- inputPanel( -->
<!--   selectInput(inputId = "sel_point", label = "Select Factor:", choices =natural_var, selected = natural_var[1]), -->
<!--   selectInput(inputId = "sum_avg", label = "conflict level:", choices =choice, selected = choice[1]) -->
<!-- ) -->



<!-- renderPlot({ -->

<!--   var = input$sel_point -->
<!--   plot_data <- data[,.("point" = get(var), ACTION_ANY)]%>% -->
<!--     group_by(point) %>% -->
<!--     summarise(Total = sum(ACTION_ANY), count = n()) %>% -->
<!--     mutate(Average = Total/count) %>% -->
<!--     arrange(point) -->

<!--   if (input$sum_avg == "Total"){ -->
<!--     ggplot(plot_data, aes(x = point, y = Total)) + -->
<!--       geom_line() + -->
<!--       theme_common + -->
<!--       labs(y = "Total number of Conflict incidents", x =var ) +  -->
<!--       scale_y_continuous(breaks= pretty_breaks()) -->
<!--   } -->
<!--   else if (input$sum_avg == "Average"){ -->
<!--     ggplot(plot_data, aes(x = point, y = Average)) + -->
<!--       geom_line() + -->
<!--       theme_common + -->
<!--       labs(y = "Average number of Conflict incidents", x =var) +  -->
<!--       scale_y_continuous(breaks= pretty_breaks()) -->
<!--   } -->
<!-- } -->
<!-- )  -->
<!-- ``` -->

Chorolpleth
==================================================

Row {data-heights = 500}
--------------------------------------------------



```{r}
all_var <-  c("TEMP", "RAIN", "Maize", "Millet", "Rice", "Sorghum", "biomass", "ACTION_ANY")

years = unique(data$YEAR)
month = 1:12
inputPanel(
  sliderInput(inputId = "choro_year", label = "Year", min = min(data[,YEAR])+1, max = max(data[,YEAR]), value = min(data[,YEAR]), step = 1),
  sliderInput(inputId = "choro_month", label = "Month", min = 1, max = 12, value = 1, step = 1),
  selectInput(inputId = "choro_feature", label = "Label:", choices =all_var, selected = all_var[1])
  
  
)



renderPlot({
  var = input$choro_feature
  year_mon = paste(input$choro_year,sprintf("%02d", input$choro_month),sep ="")
  # var = "TEMP"
  # year_mon= "200303"
  if (var == "RAIN")
  {
    high_col = "#09219F"
    low_col = "#ADD8E6"
    tit = "Rain in mm"
  }
  else if (var == "biomass")
  {
    high_col = "#04751b"
    low_col = "#A7EC6C"
    tit = "Biomass cover"
  }
  else
  {
    high_col = "#D20A04"
    low_col = "#ffe8b8"
    if (var == "TEMP")
    {
      tit = "Temperature in Celcius"
    }
    else
    {
      tit = "Number of Conflicts"
    }
    
  }
  
  
  for_val = arrange(data %>%
                     filter(!is.na(get(var))) %>%
                     mutate(id = as.character(ID_2 + 1)) %>%
                     group_by(NAME_2, id, YRMO) %>%
                     summarise(val = mean(get(var))), id)
  
  min_val = min(for_val$val, na.rm = TRUE) 
  max_val = max(for_val$val, na.rm = TRUE)
   
  second =  for_val %>%
    filter(YRMO == year_mon)
  dataframe = merge.data.frame(mydf,second, by = "id", all.x = TRUE)
  dataframe = dataframe[order(dataframe$id,dataframe$order),]

  
  
  map = ggplot(data =dataframe,aes(x= long, y=lat, group = group))
  map + 
    geom_polygon(aes(fill = val),color = 'white', size = 0.05) +
    scale_fill_gradient(high = high_col, low = low_col, guide = "colourbar", limits = c(min_val,max_val))+
    coord_fixed(1.3) +
    guides(fill=guide_colorbar(title=tit))  +
    theme_bare
}
) 
```




Prices- Trends
==================================================

Row {data-heights = 500}
--------------------------------------------------


```{r}

price_var <-  c("Maize (local) - Retail", "Rice (imported) - Retail", "Sorghum - Retail",
                "Rice (local) - Retail", "Millet - Retail", "Maize (imported) - Retail",
                "Sorghum (imported) - Retail")

inputPanel(
  selectInput(inputId = "price_tab", label = "Select Product", choices = price_var, multiple = TRUE, width = '300%'),
  sliderInput(inputId = "price_date", label = "Year Range", min = 2000, max = 2017, value = c(2010,2014), step = 1))



renderPlot({
  
  input$choro_feature
  t.data<-price_data[,c(1,2,5,8,17)]
  t.data$date<-mdy(t.data$date)
  min_date = paste(input$price_date[1],"-01-01", sep = "")
  max_date = paste(input$price_date[2],"-12-31", sep = "")
  t.data<-t.data[date >= min_date & date <= max_date &
                   cmname  %in% input$price_tab ,]
  agg.all.prod = t.data %>%
    group_by(date,cmname) %>%
    summarise(mean_cost = mean(price, na.rm = TRUE))
  names(agg.all.prod)<-c("date","Product","mean_cost")
  ggplot(agg.all.prod, aes(x=date, y=mean_cost, color=Product))+
    geom_line()+
    labs(y = "Mean Price across country", x ="Year" )+
    theme_common + 
    theme(legend.text=element_text(size=14),
  legend.title=element_text(size=16))



}
) 
